---
title: "Tutorial Week 3"
author: "SID 313010374"
date: "August 14, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Computer Exercises


```{r}
su <- survival
boxplot(su, horizontal = TRUE)
qqnorm(su)
```
From this boxplot we can see that the survival rates have a substantial right-hand tail, i.e are skewed to the right.
From the qqplot we can see that this distribution is likely not normal, as in a normal qqplot the line of quantiles would be straight. 

```{r}
mean(su)
var(su)
```
This is a one-sided test of mean with $\mu = 160$.
The test statistic is as follows:
```{r}
t.obs = (mean(su) - 160)/(sqrt(var(su)/length(su)))
t.obs
```
Finding the p-value is then as follows:
```{r}
pt(t.obs, length(su) - 1)
```
This p-value is not heaps strong evidence that the mean is less than 160. 

I already used a t-test.
The p-values would be basically the same though, since n > 30 and so the t-distribution with 71 degrees of freedom is almost exactly normal.

###Critical Values

```{r}
crit.tdist = (qt(0.05, 71))*sqrt(var(su))/sqrt(length(su)) + 160
crit.normdist = qnorm(0.05)*sqrt(var(su))/sqrt(length(su)) + 160
crit.tdist
crit.normdist
```
The critical values are almost indistinguishable, and so we don't really care whether we use the t-distribtion or the normal distribution. By either of these critical values, the observed sample mean is not significant evidence.
```{r}
su1 <- su
su1[4] = 2000
mean(su1)
```
This new data point (which seems to be a very old mouse) skews the sample average a lot. It isn't significant in this instance.





