---
title: "Tutorial Week 2"
author: "Arthur Thiele"
date: "August 7, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Computer Exercises, Week 2

1. a)

```{r}
pnorm(1.25)
pnorm(1.23, mean = 1) - pnorm(0.5, mean = 1)
pt(2.353, df = 3)
pt(1.476, df = 5)- pt(-1.476, df = 5)
```

b)
```{r}
qt(0.05, df = 8)
qt(0.25, df = 7)
qnorm(0.05)
abs(qnorm(0.025))
```


2. a)

```{r}
data <- read.csv("amp.csv")
summary(data)
data
```
b)
Since these tests are using different methods but on the same tablet (discussed with tutor Connor Smith), the null hypothesis is that there isn't a substantive difference between the measurement. 
If data[1] = X, data[2] = Y,
$$X_i - Y_i = d_i$$

Null Hypothesis $H_0$: $\mu_d = 0$
Alternative Hypothesis $H_1$: $\mu_d \neq 0$

```{r}
method.A = data[,1]
method.B = data[,2]
ds = method.A - method.B
ds
mean(ds)
sd(ds)
```

Since there are 15 observed values, our observed test statistic is 
```{r}
T = abs(mean(ds))/(sd(ds)/sqrt(15))
T
```
This distribution then has 9 degrees of freedom, and so our p-value is:
```{r}
p = 2*(1 - pt(T, df = 14))
p
```
This is evidence that there is no significant difference between the pill-testing methods, since $p = 0.71 > 0.05$

```{r}
#toto: stemleaf, rest of tutorial

```